---
title: "PFA's results analysis"
output: html_notebook
---

Try to find relevant clusters in the GBM dataset.

## PFA results

```{r include=FALSE}
setwd('~/Documents/Local_Work/Clustering')

library(SNFtool)
library(cluster)
library(ggplot2)
source('subfonctions.R')
library(CancerSubtypes)
```

```{r}
#load the results
Y_Test <- as.matrix(read.csv("Y_Test.csv", header = FALSE))
Y_Test <- t(Y_Test)
Y_cent <- as.matrix(read.csv("Y_cent.csv", header = FALSE))
Y_cent <- t(Y_cent)
Y_norm <- as.matrix(read.csv("Y_norm.csv", header = FALSE))
Y_norm <- t(Y_norm) 
```





## SNF on GBM

```{r}
n <- 215
Knn <- 20
t <- 30
alpha <- 0.5
W <- SNFCalc(n = n, t = t, Knn = Knn, alpha = alpha)
group <- spectralClustering(W, 3)
#displayClusters(W, group)
```

It's far better with SNF but it's data that is provided by the authors of SNF method so this is not so surprising...

Let's try with the data provided by the PFA authors

# Data from PFA authors


```{r}
clusterQuality(Y_Test, 2:12)
```
```{r}
plotPC(Y_Test,1:7)

```


Let's try SNF on the data from the authors of PFA !

```{r}
names <- list('data_gene_expression.csv','data_methy_expression.csv','data_mirna_expression.csv')
datasetPFApack <- lapply(names,function(name) read.table(paste0("~/Documents/Local_Work/PFA to R/TestData/",name), header = TRUE, sep = "," ))
datasetPFApack <- lapply(datasetPFApack, function(data) {return(as.matrix(data[,-1]))})
```

```{r}
W <- SNFCalc2(datasetPFApack,10,0.5,30)

for (C in 3:10){
  group <- spectralClustering(W,C)
  displayClusters(W,group)
}
```

Not so bad, but let's see whats SNF gives on random data:

```{r}
Wtest <- matrix(rnorm(100*100),100,100)
dist <- dist2(Wtest,Wtest)
affi <- affinityMatrix(dist, K = 10)
group <- spectralClustering(affi, 6)
displayClusters(affi, group)
```





## Some tests on data

We want to see how the data are preprocessed




```{r}
source('subfonctions.R')
sd_mean(datasetPFApack)  


```
As we can see, the data is normalized !

```{r}
#Test on data list
data(dataL)
dummyDataSet <- dataL
rm(dataL)
sd_mean(dummyDataSet)
```
The dummy data set is not normalized

The GBM is supposed to be normalized but let's have a look:

```{r}
listName <- list("~/Documents/Local_Work/GBM/GLIO_Gene_Expression.txt","~/Documents/Local_Work/GBM/GLIO_Mirna_Expression.txt","~/Documents/Local_Work/GBM/GLIO_Methy_Expression.txt")
GBM_data <- lapply(listName, function(name) {return(read.table(name, header = TRUE))})
dim(GBM_data[[1]])
sd_mean(GBM_data)
```

It's normalized as well !

Let's try something: aplly PFA on dummy data:
- centered
- normalized
- raw

 
```{r}
# data(dataL)
# raw <- lapply(dataL,t)
# dim(dataL[[1]])
# normalized <- lapply(dataL, standardNormalization)
# normalized <- lapply(normalized, t)
# 
# centered <- lapply(dataL, function(data) {return(t(data) - (1/300)*t(data)%*% matrix(1,300,300))})
# 
# writer2 <- function(i,dataL,name) {
#   write.csv(dataL[[i]], paste0(name,"Data_",i,".csv"))
# }
# lapply(1:2, function(i) writer2(i,centered, "cent"))
# lapply(1:2, function(i) writer2(i,normalized, "norm"))
# lapply(1:2, function(i) writer2(i,raw, "raw"))
```

PFA DID NOT WORK with the raw data, because the algorithms need the data to be centered at least !

Let's see the other results:


```{r}
#plotPC(Y_norm, 1:4)

```
```{r}
#plotPC(Y_cent, 1:5)
```

```{r}
clusterQuality(Y_norm, 3) #3 clusters in the data
clusterQuality(Y_cent, 3)
```

## With distance matrix

```{r}
pam.clusterQuality(Y_Test, Klist = 2:5)
```














