---
title: "PFA's results analysis"
output: html_notebook
---





```{r include=FALSE}
library(SNFtool)
library(cluster)
library(ggplot2)
source('subfonctions.R')

```

```{r}
#load the results

# Y_authors is the PFA results with the data provided by the authors of PFA 
Y_authors <- as.matrix(read.csv("PFA_Results/Y_authors.csv", header = FALSE))
Y_authors <- t(Y_authors)

# Y_cent is the results of PFA with a very simple dataset provided by SNF that I centered
Y_cent <- as.matrix(read.csv("PFA_Results/Y_cent.csv", header = FALSE))
Y_cent <- t(Y_cent)

# Y_cent is the results of PFA with a very simple dataset provided by SNF that I normalized
Y_norm <- as.matrix(read.csv("PFA_Results/Y_norm.csv", header = FALSE))
Y_norm <- t(Y_norm) 

# Y_GBM is the result of PFA applied on the GBM dataset, provided buy the authors of SNF (it's a TCGA dataset)
Y_GBM <- as.matrix(read.csv("PFA_Results/Y_GBM.csv", header = FALSE))
Y_GBM <- t(Y_GBM)
```
# Data from PFA authors


First, let's see the first principal components:

```{r}
plotPC(Y_authors, 1:7)
```

Then let's see the silhouette plot for a various number of clusters:

```{r}
clusterQuality(Y_authors, 2:12)
```



## SNF on PFA authors' data


Let's try SNF on the data from the authors of PFA !

```{r}

names <- list('Raw_Data/data_gene_expression.csv','Raw_Data/data_methy_expression.csv','Raw_Data/data_mirna_expression.csv')
datasetPFApack <- lapply(names,function(name) read.table(name, header = TRUE, sep = "," ))
datasetPFApack <- lapply(datasetPFApack, function(data) {return(as.matrix(data[,-1]))})
```

```{r}
#parameters for SNF:
Knn <- 10 
alpha <- 0.5
t <- 30 
W <- SNFCalc2(datasetPFApack, Knn, alpha, t)

for (C in 3:10){
  group <- spectralClustering(W,C)
  displayClusters(W,group)
}
```
## SNF on random data

Not so bad, but let's see whats SNF gives on random data:

```{r}
Wtest <- matrix(rnorm(100*100),100,100)
dist <- dist2(Wtest,Wtest)
affi <- affinityMatrix(dist, K = 10)
group <- spectralClustering(affi, 6)
displayClusters(affi, group)
```





## Distribution of our datasets

We want to see how the data are preprocessed


```{r}
sd_mean(datasetPFApack)  
```
As we can see, the data is normalized !

```{r}
#Test on data from SNFtool
data(dataL)
dummyDataSet <- dataL
rm(dataL)
sd_mean(dummyDataSet)
```
The dummy data set is not normalized

The GBM is supposed to be normalized but let's have a look:

```{r}
listName <- list("Raw_Data/GLIO_Gene_Expression.txt","Raw_Data/GLIO_Mirna_Expression.txt","Raw_Data/GLIO_Methy_Expression.txt")
GBM_data <- lapply(listName, function(name) {return(read.table(name, header = TRUE))})
sd_mean(GBM_data)
```

It's normalized as well !

## How preprocessing impact the results

Let's try something: aplly PFA on dummy data:
- centered
- normalized
- raw

 
```{r}
# Here is the process to write the data to use MATLAB to apply PFA:
# data(dataL)
# raw <- lapply(dataL,t)
# dim(dataL[[1]])
# normalized <- lapply(dataL, standardNormalization)
# normalized <- lapply(normalized, t)
# 
# centered <- lapply(dataL, function(data) {return(t(data) - (1/300)*t(data)%*% matrix(1,300,300))})
# 
# writer2 <- function(i,dataL,name) {
#   write.csv(dataL[[i]], paste0(name,"Data_",i,".csv"))
# }
# lapply(1:2, function(i) writer2(i,centered, "cent"))
# lapply(1:2, function(i) writer2(i,normalized, "norm"))
# lapply(1:2, function(i) writer2(i,raw, "raw"))
```

PFA DID NOT WORK with the raw data, because the algorithms need the data to be centered at least !

Let's see the other results:


```{r}
plotPC(Y_norm, 1:4)
```

```{r}
plotPC(Y_cent, 1:5)
```


```{r}
clusterQuality(Y_norm, 3) #3 clusters in the data
clusterQuality(Y_cent, 3)
```


Let's try 

## Clustering with distance matrix, using daisy and pam from cluster package

```{r}
pam.clusterQuality(Y_Test, Klist = 2:5)
```














